---
title: "Investigating whether T1D models can identify T2-misdiagnoses."
author: "Ethan de Villiers"
date: "`r Sys.Date()`"
output: html_document
---
# Introduction


## Init

``` {r Packages}
library(tidyverse) # streamlining R coding since 2016
library(rio) # Import/Output master package
library(psych) # Essential for descriptive stats
library(pROC) # ROC curves and such.
library (rsq) # Used for R-squared values
library(ggplot2) # Advanced Graphs
library(tableone) # Nice descriptives for tables
library(rms) # Val.prob mainly
# library(val.prob) Out dated for this version of R - useful for calibration 
```

``` {r ImportingData}
filepath = 'startight Aug 22 comma separated.csv'
my_data <- import(filepath)

#> View(my_data)
```

## Prepping Data

Notes on Data
- age_atdiag is the exact patient age in double form
- AgeatDiagnosis is the patient age in int form (used)
- In equations where AGE is used, AgeatDiag was used instead - need to fix!
- no current clean GAD, ZNT8 code
- Islet autoantibodies were considered positive if: 
  - GADA ≥11 units/mL, IA2A ≥7.5 units/mL and ZNT8A ≥65 units/mL in those aged up to 30 years and ≥10 units/mL in those aged ≥30 years (17, 18)
- GRS Scores:
  - Correct GRS version = variable: "GRS"
  - No current, calibrated/standardised GRS scores against a type-1 enriched cohort

``` {r Cleaning and Prepping Data}
# Creating Anibody columns ####
#New column GADA_Status will default to NA, and if negative = 0, positive = 1
my_data = my_data %>%
  mutate(GAD_status = ifelse(GAD == 'negative', 0, NA)) %>%
  mutate(GAD_status = ifelse(grepl("[0-9]",GAD) & as.numeric(GAD) >= 11, 1, GAD_status))

#New column IA2_status will default to NA, and if negative = 0, positive = 1
my_data = my_data %>%
  mutate(IA2_status = ifelse(IA2 == 'negative', 0, NA)) %>%
  mutate(IA2_status = ifelse(grepl("[0-9]",IA2) & as.numeric(IA2) >= 7.5, 1, IA2_status))

#New column ZNT8_Status will default to NA, and if negative = 0, positive = 1
my_data = my_data %>%
  mutate(ZNT_status = ifelse(ZNT8 == 'negative', 0, NA)) %>%
  mutate(ZNT_status = ifelse(grepl("[0-9]",ZNT8) & as.numeric(ZNT8) >= 65, 1, ZNT_status))

#Filling in BMI for missing values
my_data = my_data %>%
  mutate(BMI = ifelse(is.na(BMI), Weight / (Height^2), BMI))

#Creating column for how many antibodies a patient has, sum()
my_data$Number_Antibodies = rowSums(my_data[,c("GAD_status", "IA2_status", "ZNT_status")], na.rm=TRUE)


# Calibrating GRS-Scores ####
#Creating Type-1 enriched cohort
type_1_control_cohort = my_data %>%
  filter(Insulin == "Yes" & Number_Antibodies >= 2 & Type_of_diabetes == "Type 1") %>%
  filter(SCORE != '' & !is.na(SCORE)) # n = 456

#Calibrating GRS-Scores (pnorm())
my_data$Calibrated_GRS_Centiles = pnorm(my_data$SCORE, mean = mean(type_1_control_cohort$SCORE), sd = sd(type_1_control_cohort$SCORE))

#Calculating Time To Insulin - Date_of_diagnosis until Date_continuous insulin
my_data = my_data %>%
  mutate(Time_to_insulin = difftime(
    as.Date(Date_continuous_insulin, "%d-%b-%y"),
    as.Date(DateofDiagnosis, "%d-%b-%y"),
    units = "weeks")
  ) %>%
  mutate(Time_to_insulin = as.numeric(Time_to_insulin)) %>%
  mutate(Time_to_insulin = ifelse(Time_to_insulin < 0, 0, Time_to_insulin))

```


progressed = V3 

duration of follow up = 







``` {r Generating Model Probabilities}
# Clin F Model = 37.94 + (-5.09 * log(age at diagnosis)) + (-6.34 * log(BMI))
# Clin F + GAD Model = 34.8057844720 + (-4.801441792 * log (Age at diagnosis)) + (-5.980577792 * log(BMI)) + (2.937107976 * GADA)
# Clin F + IA2 Model = 37.26905033 + (3.194096 * IA2† ) + (-5.047657308 * Log(Age)) + (-6.287258808 * Log(BMI))
# Clin F + Antibodies (ZNT8/IA2) = 33.49649577 + (-4.665598345 * Log(Age)) + (-5.81137397 * Log(BMI)) + (3.082366 * AntiStatus1‡) + (3.494462 * AntiStatus2‡) + (4.350717 * AntiStatus3‡)
# Clin F + Anti + GRS = 21.57649882 + (-4.086215772 * log(Age)) + (-5.096252172 * log(BMI)) + (2.702010666 * [GAD POSITIVE ONLY 1 OR 0]) + (3.063255174 * [IA2 POSITIVE ONLY 1 OR 0]) + (3.813850704 * [BOTH GAD AND IA2 POSITIVE 1 OR 0]) + (30.11052 * GRS)


my_data = my_data %>% # First Model: Clinical Features alone (Age + BMI)
  mutate( logOR_clinF = 37.94 + (-5.09*log(AgeatDiagnosis)) + (-6.34 * log(BMI)) )

my_data = my_data %>% # Second Model: ClinF and GAD (Age, BMI, GAD)
  mutate( logOR_clinF_GAD = 34.8057844720 + (-4.801441792 * log (AgeatDiagnosis)) + (-5.980577792 * log(BMI)) + (2.937107976 * GAD_status))

my_data = my_data %>% # Third Model: ClinF and IA2 (Age, BMI, IA2)
  mutate( logOR_clinF_IA2 = 37.26905033 + (3.194096 * IA2_status ) + (-5.047657308 * log(AgeatDiagnosis)) + (-6.287258808 * log(BMI)))
  
my_data = my_data %>% # Fourth Model: ClinF and Antibodies (Age, BMI, GAD, IA2)
  mutate( logOR_clinF_Antibodies = 33.49649577 +
            (-4.665598345 * log(AgeatDiagnosis)) +
            (-5.81137397 * log(BMI)) +
            (3.082366 * GAD_status) +
            (3.494462 * IA2_status) +
            (4.350717 * ifelse(Number_Antibodies >= 2, 1, 0))
  )

my_data = my_data %>% # Fifth Model: ClinF + Anti + GRS (Age, BMI, GAD, IA2, GRS)
  mutate( logOR_clinF_antiGRS = 21.57649882 +
            (-4.086215772 * log(AgeatDiagnosis)) +
            (-5.096252172 * log(BMI)) +
            (2.702010666 * GAD_status) +
            (3.063255174 * IA2_status) +
            (3.813850704 * ifelse(Number_Antibodies >= 2, 1, 0)) +
            (30.11052 * GRS)
  )

```

``` {r Converting logOdds Ratio}
# exp(LogOR) / (1 + exp(LogOR)

my_data = my_data %>%
  mutate(model_clinF = exp(logOR_clinF) / (1 + exp(logOR_clinF)))

my_data = my_data %>%
  mutate(model_clinF_GAD = exp(logOR_clinF_GAD) / (1 + exp(logOR_clinF_GAD)))

my_data = my_data %>%
  mutate(model_clinF_IA2 = exp(logOR_clinF_IA2) / (1 + exp(logOR_clinF_IA2)))

my_data = my_data %>%
  mutate(model_clinF_Anti = exp(logOR_clinF_Antibodies) / (1 + exp(logOR_clinF_Antibodies)))

my_data = my_data %>%
  mutate(model_clinF_AntiGRS = exp(logOR_clinF_antiGRS) / (1 + exp(logOR_clinF_antiGRS)))

```

``` {r Type-2 Cohort building}
# Cohort = not initially treated with insulin
Type2_cohort = my_data %>%
  filter(Initial_diabetes_Insulin != "Insulin" & Insulin != "Yes")

#> Creating binary outcome to see if patients progressed
#> Progression = Visit2 or Visit3 insulin, and more than 1 week time to Insulin
#> Ensure anyone with Time_to_insulin variable is at least 1 week
#>  - Not super important because only 3 people have Time_to_insulin data
Type2_cohort = Type2_cohort %>%
  mutate(progressed = ifelse((V3Insulin == "Yes" | V2Insulin == "Yes"), 1, 0)) %>% # Calculating progressed
  mutate(progressed = ifelse(!is.na(Time_to_insulin) & Time_to_insulin <= 1, 0, progressed) )# Ensure at least 1 week Time_to_insulin


#Descriptives
type = Type2_cohort %>%
  select(Time_to_insulin, AgeatDiagnosis, BMI, GRS, HbA1c_at_diagnosis) %>%
  describe()

nrow(
  Type2_cohort %>%
    filter(Time_to_insulin <= 156)
)

```

## Data Analysis

###Descriptive Statistics
``` {r Type-2 Cohort Baseline Table}

table = print(
  CreateTableOne(
    data=Type2_cohort,
    vars = c("BMI", "AgeatDiagnosis", "GRS", "HbA1c_at_diagnosis", "model_clinF",
             "model_clinF_GAD", "model_clinF_IA2", "model_clinF_Anti",
             "model_clinF_AntiGRS", "Number_Antibodies"),
    strata = "progressed"
  ),
  test = FALSE,
  noSpaces = TRUE
)

write.csv(table, file = "testTable.csv")
#> Take .CSV file and upload text to: 
#> https://www.becsv.com/csv-table.php
#> Generate and HTML table, and download to an .htm document
#> Open doc and copy/paste HTML table into word --> powerpoint :)
#> OR open .csv in Excel and copy paste across

#> Calculating How many were single/double antibody positive/negative
nrow(
  Type2_cohort %>%
    filter(progressed == 0) %>%
    filter(Number_Antibodies  >= 2)
)

```

### Models Section

``` {r Creating Dataframe for ROC Cohort}
roc_data = Type2_cohort %>%
  filter(!is.na(progressed) &!is.na(model_clinF) & !is.na(model_clinF_Anti) &
           !is.na(model_clinF_AntiGRS) & !is.na(model_clinF_GAD) &
           !is.na(model_clinF_IA2) )

# nrow(roc_data %>% filter(progressed == 1))
```

``` {r 1: Clinical Features Model}
#> This section dedicated to the Clin F slide
#> Incorporates: ROC, Calibration, and ggViolin
Type2_cohort$model_clinF

# Distribution: ggViolin
ggplot(Type2_cohort, aes(x=as.factor(progressed), y=model_clinF)) + 
  geom_violin() +
  stat_summary(fun.y=mean, geom="point", shape=23, size=2) +
  labs(title = "Clinical Features Model Distribution") +
  ylab("Clinical Features Model Probability") +
  xlab("Outcomes")

#Distribution 2.0: Boxplot
ggplot(Type2_cohort, aes(as.factor(progressed), model_clinF)) +
  geom_boxplot() +
  xlab("Progressed (0=False)")

# ROC AUC
glm.fit = glm(roc_data$progressed ~ roc_data$model_clinF, family = binomial())
plot.new()
lines(roc_data$model_clinF, glm.fit$fitted.values)

(roc = roc(roc_data$progressed, glm.fit$fitted.values, auc=TRUE, plot=TRUE))

coords(roc, x='best')

# Calibration
val.prob(roc_data$model_clinF, roc_data$progressed)

```

``` {r 2: Clin F + GAD Model}
#> This section dedicated to the Clin F + slide
#> Incorporates: ROC, Calibration, and ggViolin
Type2_cohort$model_clinF_GAD

#Distribution 2.0: Boxplot
ggplot(Type2_cohort, aes(as.factor(progressed), model_clinF_GAD)) +
  geom_boxplot() +
  xlab("Progressed (0=False)")

# ROC AUC
glm.fit = glm(roc_data$progressed ~ roc_data$model_clinF_GAD, family = binomial())
plot.new()
lines(roc_data$model_clinF_GAD, glm.fit$fitted.values)

(roc = roc(roc_data$progressed, glm.fit$fitted.values, auc=TRUE, plot=TRUE))

coords(roc, x='best')

# Calibration
val.prob(roc_data$model_clinF_GAD, roc_data$progressed)
```

``` {r 3: Clin F + IA2 Model}
#> This section dedicated to the Clin F + slide
#> Incorporates: ROC, Calibration, and ggViolin
Type2_cohort$model_clinF_IA2

#Distribution 2.0: Boxplot
ggplot(Type2_cohort, aes(as.factor(progressed), model_clinF_IA2)) +
  geom_boxplot() +
  xlab("Progressed (0=False)")

# ROC AUC
glm.fit = glm(roc_data$progressed ~ roc_data$model_clinF_IA2, family = binomial())
plot.new()
lines(roc_data$model_clinF_IA2, glm.fit$fitted.values)

(roc = roc(roc_data$progressed, glm.fit$fitted.values, auc=TRUE, plot=TRUE))

coords(roc, x='best')

#Calibration
val.prob(roc_data$model_clinF_IA2, roc_data$progressed)
```

``` {r 4: Clin F + GAD and IA2 Model}
#> This section dedicated to the Clin F + slide
#> Incorporates: ROC, Calibration, and ggViolin
Type2_cohort$model_clinF_Anti

#Distribution 2.0: Boxplot
ggplot(Type2_cohort, aes(as.factor(progressed), model_clinF_Anti)) +
  geom_boxplot() +
  xlab("Progressed (0=False)")

# ROC AUC
glm.fit = glm(roc_data$progressed ~ roc_data$model_clinF_Anti, family = binomial())
plot.new()
lines(roc_data$model_clinF_Anti, glm.fit$fitted.values)

(roc = roc(roc_data$progressed, glm.fit$fitted.values, auc=TRUE, plot=TRUE))

coords(roc, x='best')

#Calibration
val.prob(roc_data$model_clinF_Anti, roc_data$progressed)
```

``` {r 5: Clin F + Anti + GRS Model}
#> This section dedicated to the Clin F + slide
#> Incorporates: ROC, Calibration, and ggViolin
Type2_cohort$model_clinF_AntiGRS

#Distribution 2.0: Boxplot
ggplot(Type2_cohort, aes(as.factor(progressed), model_clinF_AntiGRS)) +
  geom_boxplot() +
  xlab("Progressed (0=False)")

#ROC AUC

glm.fit = glm(roc_data$progressed ~ roc_data$model_clinF_AntiGRS, family = binomial())
plot.new()
lines(roc_data$model_clinF_AntiGRS, glm.fit$fitted.values)

(roc = roc(roc_data$progressed, glm.fit$fitted.values, auc=TRUE, plot=TRUE))

coords(roc, x='best')


#Calibration
val.prob(roc_data$model_clinF_AntiGRS, roc_data$progressed)
```

``` {r Investigating Antibodies for Comparison}
#> AUC ROC for Antibodies to compare
roc_data = Type2_cohort %>%
  filter(!is.na(Number_Antibodies) )

glm.fit = glm(roc_data$progressed ~ roc_data$Number_Antibodies, family = binomial())
plot.new()
lines(roc_data$Number_Antibodies, glm.fit$fitted.values)

(roc = roc(roc_data$progressed, glm.fit$fitted.values, auc=TRUE, plot=TRUE))

coords(roc, x='best')

```

```{r Graphing Model Distributions - LEGACY}

Type2_cohort %>%
  select(model_clinF, model_clinF_GAD, model_clinF_IA2, model_clinF_Anti, model_clinF_AntiGRS, Time_to_insulin) %>%
  mutate(Time_to_insulin = ifelse(!is.na(Time_to_insulin), "Progressed", "Did not progress")) %>%
  rename("Clin Features Model" = "model_clinF") %>%
  rename("Clin + GAD" = "model_clinF_GAD") %>%
  rename("Clin + IA2" = "model_clinF_IA2") %>%
  rename("Clin + Antibodies" = "model_clinF_Anti") %>%
  rename("Clin + Anti + GRS" = "model_clinF_AntiGRS") %>%
  gather(key = key, value = value, -Time_to_insulin) %>%
  ggplot2::ggplot() +
  geom_violin(aes(x = key, y = value,)) +
  xlab('Models') +
  ylab('Probability') +
  geom_smooth(aes(x = key, y = value), method = 'lm') +
  facet_wrap(~ Time_to_insulin)

```

``` {r Exploring Clin + Anti + GRS Deciles - OPTIONAL}
#> Primary aim of this section is to explore why the model was able to detect some
#> individuals who progressed, but not others
#> So looking at model deciles within the progressed cohort

#> Making temp cohort for desc analysis
type2_progressed = Type2_cohort %>%
  filter(progressed == "Progressed") %>%
  mutate(decile = dplyr::ntile(model_clinF_AntiGRS, 10))

table = print(
  CreateTableOne(
    data=type2_progressed,
    vars = c("BMI", "AgeatDiagnosis", "GRS", "HbA1c_at_diagnosis", "model_clinF",
             "model_clinF_GAD", "model_clinF_IA2", "model_clinF_Anti",
             "model_clinF_AntiGRS", "Number_Antibodies"),
    strata = "decile"
  ),
  test = FALSE,
  noSpaces = TRUE
)

write.csv(table, file = "testTable.csv")

#Removing temporary variables
remove(table)
remove(type2_progressed)
```

``` {r Cleaning environment}
remove(roc)
remove(roc_data)
```



## Unused Legacy Code
``` {r Legacy Unused Code}
#### Graphing Violion models against eachother #####################
#> Clin features model
#> Clin features + autoantibodies (GAD IA2)
#> compared using gg VIOLIN Plot
not_insulin %>%
  filter(!is.na(Model4Prob) & !is.na(Model1Prob) & !is.na(Model5Prob)) %>%
  select(Model1Prob, Model4Prob, Model5Prob) %>%
  rename("Clin Features Model" = "Model1Prob") %>%
  rename("Clin + Antibody Model" = "Model4Prob") %>%
  rename("Clin + Anti + GRS Model" = "Model5Prob") %>%
  gather() %>%
  ggplot2::ggplot() +
  geom_violin(aes(x = key, y = value)) +
  xlab('Models') +
  ylab('Probability') +
  geom_smooth(aes(x = key, y = value), method = 'lm')

#### Obtaining P-value for ROC comparisons
roc.test(roc, roc1)

################################################################################
################# Sub Investigation: Clin Features Model #######################
################ Able to Detect Antibody Positive Patients #####################
################################################################################
### - Clinical Model distinguishes pretty well for those who would be 
###   antibody positive
###    > Antibody positive OUT OF ALL 3 (GAD, IA2, ZNT8)
### - Therefore Clin model can be step 1 of 2 step process:
###    > Patient qualifies for antibody testing from Clinical Model
###    > Patient's antibody results come back and interpreted in second model
###    > future: create new model based on HOW MANY antibodies are positive
### - To test this:
###    > AUC ROC curve for Clinical Features model and outcome is antibody +
###    > Calibration plot for the same
################################################################################
# AUC ROC Curve for Antibody #################################
#Estabishing outcome = if ANY 3 antibody+ is positive outcome
not_insulin = not_insulin %>%
  mutate(antibody_positive = ifelse(GADA_Status == 1 | IA2A_Status == 1 | ZNT8_Status == 1, 1, 0))

#Estabishing outcome = if ALL 3 antibody- is negative outcome
not_insulin = not_insulin %>%
  mutate(antibody_positive = ifelse(GADA_Status == 0 & IA2A_Status == 0 & ZNT8_Status == 0, 0, 1))

#Filtering to ensure equal length
roc_data = not_insulin %>%
  filter(!is.na(antibody_positive) & !is.na(Model1Prob))

#Storing the logistic regression results
glm.fit = glm(roc_data$antibody_positive ~ roc_data$Model1Prob, family = binomial())
plot.new()
lines(roc_data$Model4Prob, glm.fit$fitted.values)

(roc = roc(roc_data$antibody_positive, glm.fit$fitted.values,
           #auc.polygon=TRUE,
           plot=TRUE,
           #smoothed=TRUE,
           #ci=TRUE,
           #ci.alpha = 0.9,
           #max.auc.polygon=TRUE,
           #print.auc=TRUE,
           #show.thres=TRUE
           ))

#Getting threshold, sensitivity and specificity
coords(roc, x='best')




# Clin Features Calibration #############################
deciles = list(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0)
results = list()

for (x in 1:10){
  # Need to handle first and last number specially
  if (x == 1) {
    print('# Of patients with Antibodies within first Decile = ')
    total = not_insulin %>%
      filter(Model1Prob <= 0.1) %>%
      nrow()
    
    antibody = not_insulin %>%
      filter(Model1Prob <= 0.1 & antibody_positive == 1) %>%
      nrow()
    results[1] = antibody/total
    # Need to handle first and last number specially
  } 
  else if (x == 10){
    print('# Of patients progressed to Insulin within last Decile = ')
    total = not_insulin %>%
      filter(Model1Prob > 0.9) %>%
      nrow()
    
    antibody = not_insulin %>%
      filter(Model1Prob > 0.9 & antibody_positive == 1) %>%
      nrow()
    results[10] = antibody / total
    # Index 2-9 = core loop
  } 
  else {
    print(paste('# Of patients antibody positive within Decile: ', x, ' = '))
    total = not_insulin %>%
      filter(Model1Prob > deciles[x-1] & Model1Prob <= deciles[x]) %>%
      nrow()
    
    antibody = not_insulin %>%
      filter(Model1Prob > deciles[x-1] & Model1Prob <= deciles[x] & antibody_positive == 1) %>%
      nrow()
    
    results[x] = antibody / total
  }
}

plot(deciles, results,
     xlim = c(0,1),
     ylim = c(0,1),
     main = 'Clinical Features Model',
     xlab = 'Model Probability',
     ylab = '% antibody positive')

#For r-squared value
summary(lm(unlist(results) ~ unlist(deciles), data=not_insulin))

#graph trendline and print equation
calibration_plot = lm(unlist(results) ~ unlist(deciles), data=not_insulin)
lines(unlist(deciles),
      predict(calibration_plot),
      col = 2,
      lwd = 2)
(paste("y =", coef(calibration_plot)[[1]], "+", coef(calibration_plot)[[2]], "* x"))


################################################################################
##################### Model 4 and 5 in Antibody+ ###############################
################################################################################
### - If those are already antibody positive, is there any use in model?
### - Run model in those antibody positive and see result
################################################################################
#Filtering for only those with antibodies
roc_data = not_insulin %>%
  filter(Number_Antibodies > 0)

#Descriptive Stats ########################################
nrow(roc_data)

#look at those who did progress
roc_data %>%
  filter(progressed == 0) %>%
  select(GRS, BMI, AgeatDiagnosis, HbA1c_at_diagnosis, Model4Prob) %>%
  describe()

roc_data %>%
  filter(progressed == 0) %>%
  nrow()

#ROC #########################################
roc_data = not_insulin %>%
  filter(!is.na(progressed) & !is.na(Model4Prob) & Number_Antibodies >= 1)

#Storing the logistic regression results
glm.fit = glm(roc_data$progressed ~ roc_data$Model4Prob, family = binomial())

#Graphing ROC
plot.new()
lines(roc_data$Model4Prob, glm.fit$fitted.values)
(roc = roc(roc_data$progressed, glm.fit$fitted.values, auc=TRUE, plot=TRUE))

#Getting threshold, sensitivity and specificity
coords(roc, x='best')

# Model 5 in Antibody Positive! ROC Curve ##################################
#Storing the logistic regression results
roc_data = not_insulin %>%
  filter(!is.na(progressed) & !is.na(Model5Prob) & Number_Antibodies >= 1)

glm.fit = glm(roc_data$progressed ~ roc_data$Model5Prob, family = binomial())
plot.new()
lines(roc_data$Model5Prob, glm.fit$fitted.values)

(roc1 = roc(roc_data$progressed, glm.fit$fitted.values, auc=TRUE, plot=TRUE))

#Getting threshold, sensitivity and specificity
coords(roc, x='best')

#COmpare two ROCS for p-value
roc.test(roc, roc1)

#Calibration ####################################
deciles = list(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0)
results = list()

for (x in 1:10){
  # Need to handle first and last number specially
  if (x == 1) {
    print('# Of patients progressed to Insulin within first Decile = ')
    total = roc_data %>%
      filter(Model4Prob <= 0.1) %>%
      nrow()
    
    progressed = roc_data %>%
      filter(Model4Prob <= 0.1 & progressed == 1) %>%
      nrow()
    results[1] = progressed/total
    # Need to handle first and last number specially
  } else if (x == 10){
    print('# Of patients progressed to Insulin within last Decile = ')
    total = roc_data %>%
      filter(Model4Prob > 0.9) %>%
      nrow()
    
    progressed = roc_data %>%
      filter(Model4Prob > 0.9 & progressed == 1) %>%
      nrow()
    results[10] = progressed / total
    # Index 2-9 = core loop
  } else {
    print(paste('# Of patients progressed to Insulin within Decile: ', x, ' = '))
    total = roc_data %>%
      filter(Model4Prob > deciles[x-1] & Model4Prob <= deciles[x]) %>%
      nrow()
    
    progressed = roc_data %>%
      filter(Model4Prob > deciles[x-1] & Model4Prob <= deciles[x] & progressed == 1) %>%
      nrow()
    
    results[x] = progressed / total
  }
}

plot(deciles, results,
     xlim = c(0,1),
     ylim = c(0,1),
     main = 'Clinical Features + Antibody Model',
     xlab = 'Model Probability',
     ylab = '% progressed to insulin')

#graph trendline and print equation
calibration_plot = lm(unlist(results) ~ unlist(deciles), data=roc_data)
lines(unlist(deciles),
      predict(calibration_plot),
      col = 2,
      lwd = 2)
(paste("y =", coef(calibration_plot)[[1]], "+", coef(calibration_plot)[[2]], "* x"))

#For r-squared value
summary(lm(unlist(results) ~ unlist(deciles), data=roc_data))

#Descriptive Stats for Calibration ############################
nrow(roc_data)

#How many progressed
roc_data %>%
  filter(progressed == 1) %>%
  nrow()

#How many were over threshold
roc_data %>%
  filter(Model4Prob >= 0.1159171 & progressed == 1) %>%
  nrow()

################################################################################
################## Finding Mean duration of follow up ##########################
################################################################################
### - How long was the average time from diagnosis to final follow up?
### - A LOT of date formatting :(
################################################################################
#Create new column
not_insulin$duration_follow_up = NA

#Binary variable if they have V3 data
not_insulin$HaveV3Data = NA
not_insulin = not_insulin %>%
  mutate(HaveV3Data = ifelse(V3Date_Contacted != '' & !is.na(V3Date_Contacted), 1, 0))

#Binary variable if they have V2 data
not_insulin$HaveV2Data = NA
not_insulin = not_insulin %>%
  mutate(HaveV2Data = ifelse(V2Date_Contacted != '' & !is.na(V2Date_Contacted), 1, 0))

#Calculating difference between dates for patients who have V3
V3_patients = not_insulin %>%
  filter(HaveV3Data == 1) %>%
  filter(DateofDiagnosis != '' & !is.na(DateofDiagnosis)) %>%
  mutate(duration_follow_up = difftime(
    as.Date(V3Date_Contacted, "%m/%d/%Y"),
    as.Date(DateofDiagnosis, "%d-%B-%y"), 
    units = 'weeks'), NA)

#Calculating difference between dates for patients who dont have V3 data
V2_patients = not_insulin %>%
  filter(HaveV3Data == 0 & HaveV2Data == 1) %>%
  filter(DateofDiagnosis != '' & !is.na(DateofDiagnosis)) %>%
  mutate(duration_follow_up = difftime(
    as.Date(V2Date_Contacted, "%d-%b-%y"),
    as.Date(DateofDiagnosis, "%d-%B-%y"), 
    units = 'weeks'), NA)

updated_not_insulin = rbind.data.frame(V3_patients, V2_patients)
updated_not_insulin %>%
  mutate(duration_follow_up = as.numeric(duration_follow_up)) %>%
  select(duration_follow_up) %>%
  describe()






```

